\prefacesection{Acknowledgments}
There are many people who support and guide me towards this stage today.

The first one I want to thank is my advisor, Leonidas Guibas, who helps me not only with my research but also with my improvement of personality.
When I started my Ph.D., I have very little idea of what research is and what I should do with research. He is very patient to guide me towards the right track. Specifically, he advised me to think about the problems from a high-dimensional perspective, and showed me the importance of asking important and impactful questions, discussing and sharing research ideas, and eagerly asking for other people's opinions to improve my works. I feel that any good word is not good enough to describe Leo as my advisor, and I am very fortunate and grateful to be advised by Leo.

Many researches I have done at Stanford would not have happened without guidance from another two professors, Thomas Funkhouser and Matthias Niessner. Tom is very patient and responsible. I really enjoy working and discussing with Tom during the whole process of the research, starting from high-level ideas to technical details. I appreciate that he helped me with coding to process data as a senior professor. I am grateful that he explains in details and help me understand how I should plan for and write a good paper. I believe I improved a lot under his guidance. He makes me feel he is not only my advisor but also my friend. Generally, he is one of the best advisors that I know. Another professor I want to give special thanks is Matthias. He plays an important role in helping me to start learning techniques in 3D reconstruction and formulating my research topics. He is a cool professor with a lot of cool works, and it is my honor to have the opportunity to work with him. I also want to thank the members for my oral defense committee, including Karen Liu and Jeannette bohg as members of the reading committee, and Professor George Papanicolaou as the chair of my oral committee.

Two of my close collaborators and friends give me a lot of support and help with my research. I am very happy to work Yichao, who has similar research tastes with me. I learned advanced algorithms from him and discussed a lot with him about traditional 3D vision techniques to help me understand the fundamental problems better.
Max has a very good taste about frontier research, and I learned a lot from him about the ideas of 3D deep learning. We cooperate on several cool research projects, and we have a lot of fun traveling at different places. I want to thank all people who cooperate with me during my PhD, as well as all group members in my lab at Stanford and in Matthias's lab at TUM.

I sincerely want to acknowledge several people who guided me towards the computer graphics and vision community. During my undergraduate study, Yun Fei and Bin Wang guided me towards computer graphics. I started to learn fun 3D reconstruction techniques during my internship with Zhili Chen, Duygu Celan and Hailin Jin in Adobe research.
%
I also want to thank my middle school teachers who teach me programming and algorithms, including Libo Deng, Zailin Wu, Houcong Lin, and Jing Wang.
I sincerely thank Lei Zhuang as one of my favorite teachers who played an important role for shaping my personality. She is also the one who initially suggests me to learn programming.
I also want to thank my friends in different stages of my life. I cherish the friendships, and these friendships make me who I am.

Finally, I want to thank my family, including my Mom, my Dad, and my wife. From my Mom, I learn to be optimistic, to be confident, to pursue excellence, and to do the critical thinking without blindly following other people.
From my Dad, I learn to work hard, to think carefully before I speak, to deal with my weakness instead of ignoring it.
I sincerely want to thank my wife, who supports me during my important years in Ph.D., allowing me to work late at night and cooking nice food for me during deadlines. You showed me how the world can be so beautiful, and guided me to become peaceful, patient and friendly to the world.